### 2020-06-29 Documents/ESA/sections/LitReview.tex
Added Application Papers

Reinforcement learning extends the Markov Decision Process problem by
considering the case where the reward model is not initially known to
the agent. In a similar manner, Multi Agent Reinforcement Learning
(MARL) extends the Markov Game setting to one where the payoff
structure is not a priori knowledge.

@@

There are a number of approaches towards control systems. However, the interest of this review lies
in multi-agent systems which must operate in the face of uncertainty. As such, we focus on
stochastic and distributed control. The literature of the control community is vast and can be
divided into a number of sub-fields. We consider Distributed MPC (DMPC) and Swarm Optimal Control as
those which are particularly relevant to this study and review them in this section.

@@

Swarms are generally considered to be a special case of multi-agent systems and so, to this end,
Sahin \cite{Sahin2005} puts forward five qualities which must be satisfied for a system to be
considered a swarm. Note that Sahin's work considers swarm robotics, though these qualities apply to
any agent type (computational or biological).

@@

>>>>

Reinforcement learning extends the Markov Decision Process problem by
considering the case where the reward model is not initially known to
the agent. In a similar manner, Multi Agent Reinforcement Learning
(MARL) extends the Markov Game setting to one where the payoff
structure is not a priori knowledge. MARL has found success in a number of applications,
particularly in robotics \cite{Yang2004} and but also in sensor/communication networks and finance
\cite{Zhang2019}.

@@

There are a number of approaches towards control systems. However, the interest of this review lies
in multi-agent systems which must operate in the face of uncertainty. As such, we focus on
stochastic and distributed control. The literature of the control community is vast and can be
divided into a number of sub-fields. We consider Distributed MPC (DMPC) as
a topic which is particularly relevant to this study and provide a review in this section.

@@

Swarms are generally considered to be a special case of multi-agent systems and so, to this end,
Sahin \cite{Sahin2005} puts forward five qualities which must be satisfied for a system to be
considered a swarm. Note that Sahin's work considers swarm robotics and its applicationns, though
these qualities apply to any agent type (computational or biological).

@@

Sahin goes on to describe the typical domains of application for swarm systems, which broadly fall
into four categories:

\begin{itemize}
    \item Tasks that cover a region: Environmental Monitoring and Mapping, as well as Search and
    Rescue fall into these categories. These leverage the fact that there are many agents, in a
    distributed setting, to ensure complete coverage of an area.
    \item Tasks that are dangerous: An example would be scoping out an environment with potential
    hazards before human operators are involved.
    \item Tasks that scale-up or down: This leverages the fact that the agents are independent and
    the control methodology scales. These qualities allow the number of agents to be fluid and so
    it is possible to add more or less agents to a task as its requirements vary. An example might
    be providing emergency services to individuals in a disaster relief zone, in which initial
    population estimates may be revised as the situation progresses.
    \item Tasks that require redundancy: The fact that the system is not tied to any single point of
    failure means that a task in which an agent is vulnerable to attack (cyber or physical) may be
    tackled by a swarm.
\end{itemize}
